%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Alchemist • Technical Director (Architecture and Software Engineering)} % Job title
    {Moons Out Labs @ Moons Out} % Organization
    {Remote} % Location
    {Mar 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected scalable web applications and internal tools using TypeScript, Next.js, Tailwind CSS, Python, and V0 on Vercel.}
        \item {Developed AI-driven workflows and automations to streamline media production and client deliverables.}
        \item {Designed and managed cloud-based and on-premise infrastructure for internal software and various sites. Utilized Docker, and cloud platforms (AWS/GCP/Vercel).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Accredited Technology Instructor (Software Engineering)} % Job title
    {Nebula Academy} % Organization
    {Remote} % Location
    {Oct 2022 - Mar 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Credential Scope: Authorized to design and deliver technology-focused training programs for software engineering learners}
        \item {Instructional Expertise: Demonstrated proficiency in curriculum development, pedagogical best practices, and competency-based assessment}
        \item {Quality Assurance: Maintained standards for course effectiveness through iterative feedback, learning analytics, and continuous improvement}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Technical Lead and Co-Founder} % Job title
    {Effortless Development} % Organization
    {Brooklyn, NY} % Location
    {Jan 2020 - Jul 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed strategic technical and architectural decisions, guiding agency growth and service offerings.}
        \item {Managed and mentored cross-functional teams of developers and designers.}
        \item {Led scalable solution design across Next.js, React.js, Flutter, Tailwind CSS, and Dart.}
        \item {Oversaw client engagements, sales consultations, and project delivery.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Fellow} % Job title
    {General Assembly} % Organization
    {New York, NY} % Location
    {Dec 2019 - Mar 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Completed a 12-week immersive training (400+ hours) in full-stack development: HTML, CSS, JavaScript, React, Ruby on Rails, Express, SQL.}
        \item {Partnered with UX designers to implement accessibility enhancements on a Booking.com redesign project.}
        \item {Engaged in agile, project-based development and collaborative team workflows.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Control Non-Commissioned Officer} % Job title
    {United States Marine Corps} % Organization
    {MCAS Cherry Point, NC} % Location
    {Feb 2019 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted formal inspections and audits of aircraft electrical systems, enforcing Corps standards.}
        \item {Developed and implemented SOPs that reduced rework rates and improved repair accuracy.}
        \item {Coached junior Marines in quality control techniques; compiled performance reports for command.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Maintenance Chief} % Job title
    {United States Marine Corps} % Organization
    {MCAS Cherry Point, NC} % Location
    {Apr 2018 - Feb 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scheduled and prioritized maintenance tasks for life-support systems, optimizing equipment availability.}
        \item {Coordinated parts requisitions and repair contracts to minimize downtime of >\$7M in assets.}
        \item {Supervised and trained technicians; managed spare parts inventory and maintenance budgets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Electrical Systems Technician} % Job title
    {United States Marine Corps} % Organization
    {MCAS Cherry Point, NC} % Location
    {Sep 2015 - Apr 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed preventive and corrective maintenance on generators, pumps, and power distribution systems.}
        \item {Diagnosed electrical and mechanical malfunctions; logged work orders per technical manuals.}
        \item {Assisted senior technicians and trained new Marines on maintenance procedures.}
      \end{cvitems}
    }

\end{cventries}
