%-------------------------------------------------------------------------------
%\t VOLUNTEER SECTION
%-------------------------------------------------------------------------------
\cvsection{Volunteer Work}

\begin{cventries}
    \cventry
    {Volunteer Position} % Position
    {Organization Name} % Organization
    {Location} % Location
    {Date Range} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Description of the organization and its mission.}
        \item {Your specific role and responsibilities.}
        \item {Key activities or projects you were involved in.}
        \item {Impact of your volunteer work (e.g., number of people helped, funds raised, etc.).}
        \item {Skills developed or utilized during this experience.}
      \end{cvitems}
    }

    \cventry
    {Committee Member} % Position
    {Event/Committee Name} % Organization
    {Location} % Location
    {Date Range} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Purpose and scope of the event or committee.}
        \item {Your specific role and contributions.}
        \item {Key achievements or outcomes.}
        \item {Skills demonstrated or developed.}
      \end{cvitems}
    }

    \cventry
    {Mentor/Tutor} % Position
    {Program Name} % Organization
    {Location} % Location
    {Date Range} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Description of the mentoring/tutoring program.}
        \item {Who you mentored/tutored (e.g., high school students, college students, etc.).}
        \item {Subjects or skills you helped with.}
        \item {Impact on mentees (if known).}
      \end{cvitems}
    }

    \cventry
    {Board Member} % Position
    {Non-profit Organization} % Organization
    {Location} % Location
    {Date Range} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mission and activities of the organization.}
        \item {Your role on the board.}
        \item {Key contributions or initiatives you led.}
        \item {Impact of your service.}
      \end{cvitems}
    }
\end{cventries}
